\textbf{NBA Party}

### 2017-05-08 init_model.rnw
Added in plot of average return as a function of threshold for MLB.

<<>>=
HOURS <- 24
lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team, log(nmusicians), 0)]
@

@@

@@

<<>>=
HOURS <- 36
m <- glm(outcome == 'W' ~ I(nmusicians*(nhours.lgame <= HOURS)), 
         data = lines[season < 2017 & last.game.loc != team])

### We're only interested in making predictions when teams party.
p <- predict(m, newdata = lines[season == 2017 & nhours.lgame <= HOURS & 
                                last.game.loc != team], type = 'response')

table(round(p), lines[season == 2017 & nhours.lgame <= HOURS & 
                      last.game.loc != team, outcome])

@@

<<echo=F>>=
require(mboost)
lines[, game.time := hour(date)]

lm(demeaned.reb.per.min ~ party + lag.chg.pos + travel.dist + nhours.lgame,
   data = data[last.game.loc != team] %>% na.omit) %>%
   summary
@

@@

m <- glm(I(team.score > opponent.score) ~ party + odds + I(team == location) + 
             ndays.lgame + travel.dist + weekend,
         data = lines, family = 'binomial')
summary(m)
@

@@

### 
betting.days <- lines[year(date) == 2016][idx, date]
running.prof <- cumsum(ifelse(is.na(b), 0, b))
plot(x = 1:length(b), y = running.prof, 
     main = 'Profits over the 2016 season', 
     xlab = 'Game Number', ylab = 'Profit', type = 'l')
abline(a = 0, b = 0, lty = 3)
points(x = which.min(running.prof), y = min(running.prof), type = 'p')
text(x = which.min(running.prof), y = min(running.prof), labels = min(running.prof), pos = 2)

>>>>

<<>>=

HOURS <- 24
lines[, party := ifelse(nhours.lgame <= HOURS & last.game.loc != team, log(nmusicians), 0)]

@@

# stargazer(m, style = 'qje', single.row = T)
@

@@

<<>>=

HOURS <- 36
m <- glm(outcome == 'W' ~ party, 
         data = lines[season < 2016 & last.game.loc != team])

### We're only interested in making predictions when teams party.
p <- predict(m, newdata = lines[season == 2016 & nhours.lgame <= HOURS & 
                                last.game.loc != team], type = 'response')

idx <- which(p < 0.476)
out <- table(lines[season == 2016 & nhours.lgame <= HOURS & last.game.loc != team][idx, outcome])

(out['L'] * 100 - 110*out['W']) %>% as.numeric

@@

<<echo=F>>=
lines[, game.time := hour(date)]

m <- lm(demeaned.reb.per.min ~ party + lag.chg.pos + travel.dist + nhours.lgame,
   data = data[last.game.loc != team] %>% na.omit)

#stargazer(m, style = 'qje', single.row = T)
@

@@

m <- glm(I(team.score > opponent.score) ~ party + odds + I(team == location) + 
             ndays.lgame + travel.dist + weekend,
         data = lines, family = 'binomial')
summary(m)
# stargazer(m, style = 'qje', single.row = T)
@

@@

### 
betting.days <- lines[year(date) == 2016][idx, date]
running.prof <- cumsum(ifelse(is.na(b), 0, b))
plot(x = 1:length(b), y = running.prof, 
     main = 'Profits over the 2016 season', 
     xlab = 'Game Number', ylab = 'Profit', type = 'l')
abline(a = 0, b = 0, lty = 3)
points(x = which.min(running.prof), y = min(running.prof), type = 'p')
text(x = which.min(running.prof), y = min(running.prof), labels = min(running.prof), pos = 4)

### the following plot shows sufficient deviation from house odds to motivate
### an optimized betting strategy.
hist(p- lines[year(date) == 2016, odds])

tholds <- seq(.01, .1, by = .005)
tmp <- sapply(tholds, function(t) {
    p1 <- mapply(Predict, prediction = p[idx], 
                 vegas = lines[year(date) == 2016, odds][idx],
                 MoreArgs=list(threshold = t))
    b <- mapply(Bet, our.prediction = p1,
                actual.outcome = lines[year(date) == 2016, team.score > opponent.score][idx],
                odds = lines[year(date) == 2016, odds][idx], SIMPLIFY = T)
    return(c(sum(b, na.rm = T) / sum(!is.na(b)), sum(!is.na(b)))) # Avg profit per game.
})

plot(x = tholds, y = tmp[1, ], main = 'Return per game\nas a function of threshold', xlab = 'threshold', ylab = 'average profit')
text(x = tholds, y = tmp[1, ], labels = tmp[2, ], pos = 1)

### plot return per game as a function of difference in odds between us and vegas.
